\Large{All in the family:\\Anna and Lisa Hahner's finishing times in\\the 2016 women's Olympic marathon}

### 2017-02-03 paper/paper.tex
for david

%% Before considering results, DNF biz...

@@

Turning back to the motivation of this article, we have offered two
perspectives on Anna and Lisa Hahner'

>>>>

David---comments here?    Or above?  This is not from the simulation
--- so perhaps move to top of section??

\begin{figure}[!ht]
    \centering
    \includegraphics[keepaspectratio]{studentized_residuals.pdf}
    \caption{Studentized residuals}
    \label{fig:studentizedresiduals}
  \end{figure}

@@

Looking back at the original motivation of this article, we have
offered two perspectives on Anna and Lisa Hahner's near-simultaneous
finish in the 2016 women's Olympic marathon in Rio.  The German twins
were accused of deliberately slowing down and finishing next to each
other so as to generate media attention.  They denied this, not
entirely surprisingly,

We have offered two perspectives on the marathon, one based on
visualizations and simple calculations and a second that draws on a
simulation.  Both perspectives have the same implications, and they
are as follows.  In a global sense, the Hahner twins did not slow down
appreciably during the marathon.  Their times were not fast, but they
were within reason for runners of the Hahners' abilities.  Locally,
though, we find that the Hahner's finish was in fact contrived.  Their
finish---one second between the two women---was an extremely low
probability even.  Compared to their differences as measured by
personal best times prior to Rio, the Hahner twins difference in
finishing times was unusually compressed.  This is evidence that their
finishing had elements of intentionality---perhaps at the last minute
but intentionality nonetheless.

Now what... David?
